Supplementary Information

### 2015-09-04 manuscript/supplement.tex
A very small addition to the supplement.

    [[Explain why we were interested]]
    We were also interested [[AE wants us to say why, because curiosity isn't a good reason to do science]] 
    in the ways that scaling relationships with species richness might
    be affected by changes to the distribution of species among trophic levels. To
    that end, we repeated our analyses replacing species richness with the
    proportion of basal resources, proportion of intermediate consumers,
    or proportion of top predators. All model fitting procedures were identical to those
    described for species richness. The model simplicication procedure was similar to
    the procedure described for species richness, except that in some cases there were
    multiple models with $\delta$AIC\textless2 that shared the minimal degrees of freedom.
    In these cases, we defined the best-fitting model as the model with the lowest AIC in the
    set of models with $\delta$AIC\textless2 and the minimal degrees of freedom.

@@

    The relationships between latitude and the proportions of species at each
    trophic level were more complex than the flat relationship between latitude
    and species richness in this dataset.  The proportion of basal resources
    increased towards the poles in stream webs
    ($\beta_{Latitude:stream}$=0.011, $p$\textless0.001)  but did not vary
    with latitude in estuarine, marine, lake, or terrestrial  food webs
    ($\beta_{Latitude}$=0.001, $p$=0.080), while the proportion of
    intermediate consumers decreased towards the poles in all ecosystem types
    except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
    $\beta_{Latitude:Lake}$=0.005, $p$=0.016). The proportion of top predators
    in a food web,  meanwhile, decreased towards the poles in lake and  stream
    food webs but did not vary in other ecosystem types
    ($\beta_{Latitude}$=0.002, $p$=0.151;  $\beta_{Latitude:Lake}$=-0.006,
    $p$=0.001; and $\beta_{Latitude:stream}$=-0.007, $p$=0.006).

>>>>

    We were also interested in the ways that scaling
    relationships with species richness might
    be affected by changes to the distribution of species 
    among trophic levels. [[more justification of why]]
    To that end, we repeated our 
    analyses replacing species richness with the
    proportion of basal resources, proportion of 
    intermediate consumers, or proportion of top 
    predators. All model fitting procedures were identical 
    to those described for species richness. The model 
    simplicication procedure was similar to
    the procedure described for species richness, except 
    that in some cases there were multiple models with 
    $\delta$AIC\textless2 that shared the minimal degrees 
    of freedom. In these cases, we defined the 
    best-fitting model as the model with the lowest AIC in 
    the set of models with $\delta$AIC\textless2 and the 
    minimal degrees of freedom.

@@

    As with species richness, specialisation scaled with
    the numbers and proportions of species at each trophic
    level following a lognormal distribution.
    The relationships between latitude and the proportions of species at each
    trophic level were more complex than the flat relationship between latitude
    and species richness in this dataset.  The proportion of basal resources
    increased towards the poles in stream webs
    ($\beta_{Latitude:stream}$=0.011, $p$\textless0.001)  but did not vary
    with latitude in estuarine, marine, lake, or terrestrial  food webs
    ($\beta_{Latitude}$=0.001, $p$=0.080), while the proportion of
    intermediate consumers decreased towards the poles in all ecosystem types
    except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
    $\beta_{Latitude:Lake}$=0.005, $p$=0.016). The proportion of top predators
    in a food web,  meanwhile, decreased towards the poles in lake and  stream
    food webs but did not vary in other ecosystem types
    ($\beta_{Latitude}$=0.002, $p$=0.151;  $\beta_{Latitude:Lake}$=-0.006,
    $p$=0.001; and $\beta_{Latitude:stream}$=-0.007, $p$=0.006).
